Interpreting Random Forest Predictions for Bullet Matching Using LIME (?)

### 2018-09-25 paper/paper.Rmd
figure height and width

@@

```{r}
hamby224_explain <- readRDS("../data/hamby224_explain.rds")

@@

hamby224_test_explain %>%
  filter(set == "1", samesource == "FALSE") %>%
  ggplot(aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(bullet1 ~ bullet2, space = "free", scale = "free") + 
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(midpoint = 0)
```

>>>>

Some plots to tryout working with the new explanations...

@@

```{r, fig.width = 8, fig.height = 4}
hamby224_explain <- readRDS("../data/hamby224_explain.rds")

@@

hamby224_test_explain %>%
  filter(set == "1", samesource == "FALSE") %>%
  ggplot(aes(x = case, y = feature_desc)) + 
  geom_tile(aes(fill = feature_weight)) + 
  facet_grid(bullet1 ~ bullet2, space = "free", scale = "free") + 
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_gradient2(midpoint = 0) +
  theme(legend.position = "bottom")
```
